The Natural History of Child Signals of Need in Utila, Honduras: An Exploratory Study

### 2024-10-22 Paper.qmd
Final work on ordinal models

::: {#fig-effect_relativeneed}
```{r, fig.width= 10}
signaling_plot_need_freq
```

@@

::: {#fig-plot_relative_investment}
```{r, fig.width= 8}
plot_relative_investment
```

@@

::: {#fig-effect_last_signal_response}
```{r, fig.width= 8}
signaling_plot_last_signal_response
```

>>>>

::: {#fig-effect_relativeneed}
```{r, fig.width= 10}
# signaling_plot_need_freq
plot_need_age / plot_need_sad + ggtitle("") + plot_layout(guides = 'collect') + plot_annotation(tag_levels = "A")
```

@@

::: {#fig-plot_relative_investment}
```{r, fig.width= 8}
# plot_relative_investment
plot_invest_need
```

@@

::: {#fig-effect_last_signal_response}
```{r, fig.width= 8}
# signaling_plot_last_signal_response
plot_caregiver_punish / plot_caregiver_pain + ggtitle("") + plot_layout(guides = 'collect')
```
